---
title: "Exercise 1b"
author: "Meret Mosimann"
date: "16 September 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Exercise Description

Create an HTML document that samples 100 values from a log-normal
distribution (say, mu=1, sigma=.25); create a histogram of the
distribution and the distribution on the log scale; report the mean and
variance of the sample in line in the text.


### Generating data
```{r}
data <- rlnorm(100, mean = 1, sd = .25)
data <- as.data.frame(data)
```


### Plotting
```{r}
ggplot(data, aes(x=data)) + 
  geom_histogram(bins=12) +  
  scale_x_log10() +
  xlab('Values shown on log10 scale') +
  ylab('Count') +
  ggtitle('Randomly sampled data from log normal distribution')

```

## Reporting mean and variance

The theoretical mean ought to be 1. The mean calculated from the data is `r mean(data$data)`.\
The expected variance is \(0.25^2\), which is 0.0625. The variance from the randomly sampled data is `r var(data$data)`.
